\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-09-28 sections/tables_figures.tex
Update on Overleaf.
Add: Analysis for Figure 7 (text)
Change: Move tables and fix headers
1. Tables now occupy their own pages at the end (without page numbers)
   we just have to split those pages
2. Updated the preamble such that there are no headers anymore

  \begin{table}[H]
    \centering
    \small
    \begin{tabular}{|c|c|c|c|}
      \hline
      \textbf{Workflow step} & \textbf{Module/Condition} & \textbf{Tool/Parameter} & \textbf{References/Value} \\
      \hline
      \multirow{7}{*}{Denoising and Clustering} & \multirow{5}{*}{Denoise and Cluster} & Closed reference & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
                                                &  & Open reference & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
                                                &  & De novo & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
                                                &  & \rowcolor{lightgray} Dada2 & \cite{Callahan2016} \\
                                                &  & Deblur & \cite{Amir2017,bolyenReproducibleInteractiveScalable2019} \\
                                                \cline{2-4}
                                                & \multirow{2}{*}{Chimera checking} & Uchime-denovo & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
                                                & & \rowcolor{lightgray} Remove bimera & \cite{Callahan2016} \\
                                                \hline
      \multirow{5}{*}{Taxonomy assignment} &  \multirow{2}{*}{Query tool} & Blast & \cite{camachoBLASTArchitectureApplications2009,bokulichOptimizingTaxonomicClassification2018} \\
                                           &  & \rowcolor{lightgray} Naive bayes classifier & \cite{bokulichOptimizingTaxonomicClassification2018} \\
                                           \cline{2-4}
                                           & \multirow{3}{*}{Database} & \rowcolor{lightgray} Greengenes 13\_8 & \cite{DeSantis2006} \\
                                           & & SILVA 138 & \cite{Quast2012} \\
                                           & & NCBI RefSeq (Oct 2021) & \cite{Sayers2009} \\
      \hline
      \multirow{6}{*}{OTU processing} & \multirow{3}{*}{Filter(off)} & Prevalence threshold      & 2 / n\_samples \\
                                      & & Abundance threshold       & 0.001          \\
                                      & & Observation sum threshold & 10             \\ \cline{2-4}
                                      & \multirow{3}{*}{Filter(on)}  & \rowcolor{lightgray} Prevalence threshold      & 0.05           \\
                                      & & \rowcolor{lightgray} Abundance threshold       & 0.01           \\
                                      & & \rowcolor{lightgray} Observation sum threshold & 100            \\
      \hline
      \multirow{12}{*}{Network Inference} & \multirow{2}{*}{Bootstrapping}& fastspar\_bootstraps v1.0 & \cite{Watts2018} \\
                                          & & fastspar\_pvalues v1.0 & \cite{Watts2018} \\
                                          \cline{2-4}
                                          & \multirow{6}{*}{Direct association} & \ac{spieceasi} v1.1.2 & \cite{Kurtz2015} \\
                                          & & FlashWeave.jl v0.18.1 & \cite{tackmannRapidInferenceDirect2019} \\
                                          & & \ac{cozine} v1.0 & \cite{haCompositionalZeroinflatedNetwork2020a} \\
                                          & & \ac{harmonies} v1.0 & \cite{jiangHARMONIESHybridApproach2020} \\
                                          & & \ac{spring} v1.0.4 & \cite{yoonMicrobialNetworksSPRING2019} \\
                                          & & \ac{mldm} v1.1 & \cite{Yang2017} \\
                                          \cline{2-4}
                                          & \multirow{2}{*}{Correlation-based} & FastSpar (\ac{sparcc}) v1.0 & \cite{Watts2018} \\
                                          & & Pearson & - \\
                                          & & Spearman & - \\
                                          & & propr v2.1.2 & \cite{quinnProprRpackageIdentifying2017} \\ \cline{2-4}
                                          & \multirow{2}{*}{Consensus algorithm} & \rowcolor{lightgray} scaled-sum & 0.333 \\
                                          & & simple voting & 1.000 \\
      \hline
    \end{tabular}
    \caption{
      \textbf{Tools used in the \ac{micone} pipeline}.
      The tools highlighted in gray are the defaults for the pipeline and are recommended based on the benchmarks with the mock and synthetic datasets.
      The consensus algorithm in the \ac{ni} step incorporates all the modules (bootstrapping, direct association and correlation-based) in that step to generate the consensus network.
    }
    \label{tab:micone_tools}
  \end{table}

@@

  % \FloatBarrier
  % \newpage
  % \begin{figure}[H]
  %   \centering
  %   \includegraphics[width=1.0\linewidth]{figure7.pdf}
  % \end{figure}
  \begin{figure}[H]
    \centering
    \caption{
      \textbf{Comparison of networks generated from control and ASD samples using the \ac{micone} pipeline}.
      The networks for the control (left) and ASD (right) samples in the FMT dataset were generated using the default tools and parameters recommended by the \ac{micone} pipeline.
      There are 20 unique links in the network for control samples, 12 unique links in the network for ASD subjects and 7 edges in common between both networks.
    }
    \label{fig:figure7}
  \end{figure}

  \subsection*{Supplementary figures}

>>>>

  \begin{table}[H]
    \centering
    \caption{
      \textbf{Tools used in the \ac{micone} pipeline}.
      The tools highlighted in gray are the defaults for the pipeline and are recommended based on the benchmarks with the mock and synthetic datasets.
      The consensus algorithm in the \ac{ni} step incorporates all the modules (bootstrapping, direct association and correlation-based) in that step to generate the consensus network.
    }
    \label{tab:micone_tools}
  \end{table}

@@

  % \FloatBarrier
  % \newpage
  % \begin{figure}[H]
  %   \centering
  %   \includegraphics[width=1.0\linewidth]{figure7.pdf}
  % \end{figure}
  \begin{figure}[H]
    \centering
    \caption{
      \textbf{Comparison of networks generated from control and ASD samples using the \ac{micone} pipeline}.
      The networks for the control (left) and ASD (right) samples in the FMT dataset were generated using the default tools and parameters recommended by the \ac{micone} pipeline.
      There are 20 unique links in the network for control samples, 12 unique links in the network for ASD subjects and 7 edges in common between both networks.
      These connections can serve as potential starting points for further experimental validations or literature surveys.
    }
    \label{fig:figure7}
  \end{figure}

  \FloatBarrier
  \newpage
  \subsection*{Supplementary Tables and Figures}

  \renewcommand{\thefigure}{S\arabic{figure}}
  \setcounter{figure}{0}

  \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{table}{0}

  \begin{table}[H]
    \centering
    \caption{
      \textbf{Table of global network metrics for networks inferred from all possible combinations of tools}.
      The metrics are averaged for each tool in every step of the pipeline, therefore, all combinations of networks that use a particular tool are grouped and averaged.
    }
    \label{tab:network_metrics}
  \end{table}
